Notes on the low density parameters in {\tt MAESTRO}

### 2009-09-17 docs/lo_density/lo_density.tex
if do_eos_h_above_cutoff=T, recompute h for rho <= base_cutoff_density rather than rho < base_cutoff_density
in short, now every instance of using a cutoff density in the code is consistent between the <= and < inequalities.

@@

\item In {\tt make\_div\_coeff}, for 
  $r \ge {\tt anelastic\_cutoff\_coord}$, we set
  ${\tt div\_coeff}(n,r) = {\tt div\_coeff}(n,r-1) * \rho_0(n,r)/\rho_0(n,r-1)$.
  \MarginPar{I think we want $r > {\tt anelastic\_cutoff\_coord}$.}

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.
  \MarginPar{I think we want $r > {\tt anelastic\_cutoff\_coord}$.}

@@

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0^{\rm cart} > {\tt base\_cutoff\_density}$ 
  (in spherical).
  \MarginPar{For plane-parallel, I think we should use 
    $r \le {\tt base\_cutoff\_density\_coord}$.}

\item In {\tt mkrhohforce} for plane-parallel, for
  $r \ge {\tt base\_cutoff\_density\_coord}$, we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.
  \MarginPar{I think we want $r > {\tt base\_cutoff\_density\_coord}$.}

\item In {\tt update\_scal}, if $\rho < {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.
  \MarginPar{I think we want $\rho \le {\tt base\_cutoff\_density}$}

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.
  \MarginPar{I think this needs to be reworked to include mass up to the 
    cell-centered location of {\tt base\_cutoff\_density\_coord} for both cell 
    and edge gravity.}

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r > {\tt base\_cutoff\_density\_coord}$.

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt base\_cutoff\_density\_coord}$.
  \MarginPar{I think we want to change this to $r \le {\tt base\_cutoff\_density\_coord}$.}

>>>>

\section{Density vs. Coordinate}

Note that saying $r\ge$ {\tt anelastic\_cutoff\_coord} is analogous to saying $\rho_0(r)\le$ {\tt anelastic\_cutoff}.  Also, saying $r<$ {\tt anelastic\_cutoff\_coord} is analogous to saying $\rho_0(r)>$ {\tt anelastic\_cutoff}.  Ditto for {\tt base\_cutoff\_density} and {\tt base\_cutoff\_density\_coord}.

@@

\item In {\tt make\_div\_coeff}, for 
  $r \ge {\tt anelastic\_cutoff\_coord}$, we set
  ${\tt div\_coeff}(n,r) = {\tt div\_coeff}(n,r-1) * \rho_0(n,r)/\rho_0(n,r-1)$.

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.

@@

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for $r < {\tt base\_cutoff\_density\_coord}$
  (in plane parallel) and if $\rho_0^{\rm cart} > {\tt base\_cutoff\_density}$ 
  (in spherical).

\item In {\tt mkrhohforce} for plane-parallel, for
  $r \ge {\tt base\_cutoff\_density\_coord}$, we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

\item In {\tt update\_scal}, if $\rho \le {\tt base\_cutoff\_density}$
   and {\tt do\_eos\_h\_above\_cutoff}, we call the EOS to compute $h$.

\item In {\tt make\_grav} for spherical, we only add the enclosed mass if
  $\rho_0 > {\tt base\_cutoff\_density}$.

\item In {\tt enforce\_HSE}, we set $p_0(r+1) = p_0(r)$ for 
  $r \ge {\tt base\_cutoff\_density\_coord}$.

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt base\_cutoff\_density\_coord}$.
